An interactive environment for mapping computational structures to FPGAs

### 2016-07-07 paper/paper.tex
A few spelling checks

  FPGAs have an enormous potential in terms of computational power.
  However, they still remain hard to program even though a lot of work has been performed on translating imperative languages to hardware.
  By using a sequential language to describe parallel hardware a structural mismatch emerges.
  A lot of analysis is therefore required to determine which computations are independent and ca therefore be performed in parallel.

@@

  By applying an \emph{unfolding} transformation to the graph, a node is replaced by several copies, each representing a subset of the invocations of that node.
  This increases the space allocatd to that function, and decreases the number of node invocations per place.
  It furthermore explicitly exposes parallelism, which may be beneficial to performance.

>>>>

  FPGAs have an enormous potential in terms of computational power.
  However, they still remain hard to program even though a lot of work has been performed on translating imperative languages to hardware.
  By using a sequential language to describe parallel hardware a structural mismatch emerges.
  A lot of analysis is therefore required to determine which computations are independent and can therefore be performed in parallel.

@@

  By applying an \emph{unfolding} transformation to the graph, a node is replaced by several copies, each representing a subset of the invocations of that node.
  This increases the space allocated to that function, and decreases the number of node invocations per place.
  It furthermore explicitly exposes parallelism, which may be beneficial to performance.
